\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-27 doc/sui14/sui14.tex
first pass with rebuttals
emphasize spatial
intro shortened
update caption for teaser

\teaser{
  \centering
  \includegraphics[width=\textwidth]{figures/teaser.png}
  \caption{{\em Left}: Our head orientation-based selection techniques use an IR emitter -- multiple targets may fall within its illumination area. {\em Center}: We offer two list-based refinement techniques -- {\em Naive IR} uses alphabetical ordering; {\em Intensity IR} orders targets by IR intensity. {\em Right}: Alternatively, users can refine their selection through head orientation refinement in a quasi-mode.}
  \label{fig:teaser}
}

@@

\begin{abstract}
\input{abstract}
\end{abstract}
\vspace{-0.05in}
\keywords{
  Wearable computing; selection; glass; infrared
}
\vspace{-0.1in}
%% refer to http://www.acm.org/about/class/ccs98-html
\category{H.5.2.}{Information Interfaces and Presentation (e.g. HCI)}{Interaction styles (e.g., commands, menus, forms, direct manipulation).}

>>>>

\teaser{
  \centering
  \includegraphics[width=\textwidth]{figures/teaser.png}
  \caption{{\em Left}: Our head orientation-based selection techniques use an IR emitter -- multiple targets may fall within its illumination area. {\em Center}: We offer two list-based refinement techniques -- {\em Naive IR} uses alphabetical ordering; {\em Intensity IR} orders targets by IR intensity. {\em Right}: Using {\em Head-motion Refinement} technique, users can refine their selection through head orientation refinement in a quasi-mode when they hold the touchpad.}
  \label{fig:teaser}
}

@@

\begin{abstract}
\input{abstract}
\end{abstract}
\vspace{-0.05in}
\keywords{
  Wearable computing; spatial interaction; selection; Glass%; infrared
}
\vspace{-0.1in}
%% refer to http://www.acm.org/about/class/ccs98-html
\category{H.5.2.}{Information Interfaces and Presentation (e.g. HCI)}{Interaction styles}% (e.g., commands, menus, forms, direct manipulation).}
